Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-31 Paper/background.tex
tuned up writing and compressed the background.  SF doesn't think we need background on censorship since that is not our main focus and not required to understand the rest of the paper

The AS-layer is the highest level of organization of the Internet, with each individual AS represents a separately administered network, for example, a large ISP, a university network, or a government entity. The Border Gateway Protocol (BGP) is used to route traffic among ASes \cite{bgp}.  AS-level routes are known as \emph{paths} and are specified by routing tables stored locally in each AS. These tables express known connections to other ASes and local preferences for how data are routed, e.g., if there are multiple paths to a single destination, an AS may prefer the path that costs the least.

Because BGP is a distributed protocol, with all connectivity
information stored in the local routing tables, it is challenging to
infer the exact AS topology at any point in time.  Several strategies have been developed to infer AS topology, but none of them is perfect.  Methods that rely
on routing table information and BGP
updates suffer from the fact that BGP paths stored in routing tables
reflect only the current knowledge of a single AS about the routes
available~\cite{BGPStream}.
% FIXME: Not sure what BGPStream citation is for.  We need a different citation for RIPE unless that is what BGPStream is.
Thus one would need to use many sources to infer an accurate
picture of the BGP topology, which is not easily scalable for
global studies, particularly those looking at multiple time periods.
Similarly, methods based on empirical traceroute data are known to be incomplete or inaccurate~\cite{tracerouteProblems}.

\par AS-level studies are further complicated by the lack of ground
truth data for AS relationships and BGP paths. For AS relationships,
inference is often used based on economic considerations to classify
the relationships of ASes. This was first done by Gao \cite{gao} by
maximizing the occurances of certain economic rules on the AS graph by
choosing a particular set or relationships. This technique was only
evaluated against a single ISPs set of true relationships, however. As
part of the CAIDA project, this inference technique was extended,
leading to the CAIDA AS-relationship dataset \cite{CAIDApaper},
\cite{CAIDA}. We choose these relationships for our purposes, and they
are the current research standard.

\par Finding BGP paths is more of
a challenge. Packet based simulations, wherein BGP is simulated
directly, are computationally infeasible for the scales relevant to a
global study. An accurate, but realistic, simulation technique must be
chosen to provide useful research potential in this regard.  The
BGPSim algorithm \cite{quicksand} is one such simulation technique
that is suitable for this study's purposes. BGPSim takes a set of AS
relationships as input, such as those provided by the CAIDA dataset
\cite{CAIDA}, and returns routing trees based off of these
relationships. These paths are found via a modified breadth-first
seach (BFS) algorithm. The BFS adds edges to routing trees first
according to local preference (LP), then shortest path (SP), and
finally tiebreak (TB).  A resulting routing tree contains all the
equally reasonable paths (according to economic concerns) that exist
between source ASes (within the routing tree) to destination ASes (the
root of the routing tree). We find this technique suitable for our
purposes, so we extend BGPSim (in ways explained further in this
paper) as part of \toolname{}.

>>>>

% We already said this in the introductino
%The AS-layer is the highest level of organization of the Internet, with each
%individual AS represents a separately administered network, for example, a
%large ISP, a university network, or a government entity.
The Border Gateway
Protocol (BGP) is used to route traffic among ASes \cite{bgp}.  AS-level routes
are known as \emph{paths} and are specified by routing tables stored locally in
each AS. These tables express known connections to other ASes and local
preferences for how data are routed, e.g., if there are multiple paths to a
single destination, an AS may prefer the path that costs the least.

Because BGP is a distributed protocol, with all connectivity
information stored in the local routing tables, it is challenging to
infer the exact AS topology at any point in time.  Several strategies
have been developed, each with advantages and drawbacks. For example,
methods based on empirical traceroute data are known to be incomplete
or inaccurate~\cite{tracerouteProblems}. Similarly, methods that rely
on routing table information reflect only the current knowledge of a
single AS, or small set of ASes, about available
routes~\cite{BGPStream}, and they rely on ASes that are willing to
share their routing table information.  Many such ASes are required
% FIXME: Not sure what BGPStream citation is for.  We need a different citation for RIPE unless that is what BGPStream is.
to infer a reliable picture of the BGP topology, an approach that does not scale well for global studies over time.

\par AS-level studies are further complicated by the lack of ground
truth data for AS relationships and BGP paths. Two ASes might enter a peering relationship,
exchanging traffic but not announcing their connection. For AS relationships such as these, economic models are often used to classify
the relationships of ASes. This approach was pioneered by Gao \cite{gao}, who
assigned AS relationships that optimized certain economic rules on the AS graph.
%This technique was only
%evaluated against a single ISPs set of true relationships, however. As
This inference technique was extended by the CAIDA project,
leading to the CAIDA AS-relationship dataset \cite{CAIDApaper},
\cite{CAIDA}, which are the current research standard.
%We choose these relationships for our purposes, and they
%are the current research standard.

\par Knowing the AS topology and AS relationships is critical for finding BGP paths, but it is not sufficient because BGP does not always adopt
the shortest paths available on the
AS graph. Instead, they are determined by a combination of the dynamics of
BGP updates between ASes and the local preferences of each AS to route traffic
to destinations according to local AS policies.
%Packet based simulations, wherein BGP is simulated
%directly, are computationally infeasible for the scales relevant to a
%global study.
BGPSim is a realistic, simulation technique developed to infer likely BGP paths.~\cite{quicksand}. BGPSim takes as input a set of AS
relationships, such as those provided by the CAIDA dataset
\cite{CAIDA}, and returns routing trees based on these
relationships. A routing tree contains all
equally reasonable paths (according to economic and connectivity constraints) that between source ASes (within the routing tree) to destination ASes (the
root of the routing tree). These paths are found using a modified breadth-first
search (BFS) algorithm. The BFS adds edges to routing trees first
according to local preference (LP), then shortest path (SP), and
finally tiebreak (TB).
%We find this technique suitable \Ben[inline]{Why is it suitable?} for our
%purposes.
We adopt the basic algorithm of BGPSim
%(in ways explained further in this
%paper)
as part of \toolname{}.

\Ben[inline]{We need to discuss not only the background of BGP routing here, but 
also background about surveillance and censorship. We could probably shorten/tighten
the BGP stuff to make room.}

### 2018-07-31 Paper/intro.tex
tuned up writing and compressed the background.  SF doesn't think we need background on censorship since that is not our main focus and not required to understand the rest of the paper

Today, most such control is exercised at the country level, as
governments have recognized both the threat and the opportunity that
is posed by ubiquitous online communication. For example, much of the
organization, revolutionary momentum, and broadcasting of events
during the Arab Spring have been attributed to social media
communications through the Internet \cite{arabspring}, and several
countries sought to control these movements by disconnecting
in-country networks from the rest of the world \cite{BGPdisrupt}.
These two factors, increasing dependence on the Internet and increased
content monitoring, point to the need for improved tools and methods
for studying worldwide Internet architecture over time.  Current
methods have primarily focused on the node level (individual ASes)
rather than the country level\Steph[inline]{Josh Karlin and Jen Rexford papers are two exceptions},
they have not described how AS topology
has changed over time with respect to national boundaries, and
existing BGP simulation methods make it difficult to address 
questions such as these efficienty and at scale.

>>>>

Today, most such control is exercised at the country level, as
governments have recognized both the threat and the opportunity that
is posed by ubiquitous online communication. For example, much of the
organization, revolutionary momentum, and broadcasting of events
during the Arab Spring have been attributed to social media
communications through the Internet \cite{arabspring}, and several
countries sought to control these movements by disconnecting
in-country networks from the rest of the world \cite{BGPdisrupt}.
These two factors, increasing dependence on the Internet and increased
content monitoring, point to the need for improved tools and methods
for studying worldwide Internet structure over time.  Current
methods have primarily focused on the node level (individual ASes)
rather than the country level\Steph[inline]{Josh Karlin and Jen Rexford papers are two exceptions and maybe there are more}, 
they have not described how AS topology
has changed over time with respect to national boundaries, and
existing BGP simulation methods make it difficult to address 
questions such as these efficienty and at scale.
